**Machine learning identifies unique taxa differentiating proximal and distal human colonic microbiota**

### 2017-03-29 submission/manuscript.Rmd
manuscript updates

- colon cancer 
- right and left tumors are morphologically and genetically distinct
- the microbiome is of healthy people and patients with CRC is distinguishable at the OTU level
- specific keystone species are associated with CRC tumors
- do the populations of bacteria in the left and right colon contribute to the development of specific subtypes of CRC? 
- nearly all studies of the gut microbiome have been from shed stool or colonoscopy with bowel prep
- bowel prep changes the mucosal/fecal microbiome and what can be analyzed from it. 
- first, need to characterize healthy species that are specific to each location. then we can ask, if/how disruption affects tumorigenesis? 
- how does the microbiome vary spatially along the colon?

>>>>

- colon cancer 
- right and left tumors are morphologically and genetically distinct
- the microbiome of healthy people and patients with CRC is distinguishable at the OTU level
- specific keystone species are associated with CRC tumors
- do the populations of bacteria in the left and right colon contribute to the development of specific subtypes of CRC? 
- nearly all studies of the gut microbiome have been from shed stool or colonoscopy with bowel prep
- bowel prep changes the mucosal/fecal microbiome and what can be analyzed from it. 
- first, need to characterize healthy species that are specific to each location. then we can ask, if/how disruption affects tumorigenesis? 
- mucosal vs lumenal populations studies have also been complicated by bowel prep 
- how does the microbiome vary spatially along the colon? we know that the environment varies dramatically but we dont know how those environmental factors specifically affect bacterial populations 
- hypothesis: there are distinct bacteria on the left and right side that can be distinguished by 16S sequencing of stool
